% resume.tex
%
% (c) 2002 Matthew Boedicker <mboedick@mboedick.org> (original author) http://mboedick.org
% (c) 2003-2007 David J. Grant <davidgrant-at-gmail.com> http://www.davidgrant.ca
% (c) 2019 Lucas Saldyt <lucassaldyt@gmail.com> https://github.com/LSaldyt
%
% This work is licensed under the Creative Commons Attribution-ShareAlike 3.0 Unported License. To view a copy of this license, visit http://creativecommons.org/licenses/by-sa/3.0/ or send a letter to Creative Commons, 171 Second Street, Suite 300, San Francisco, California, 94105, USA.

\documentclass[letterpaper,11pt]{article}

%-----------------------------------------------------------
%Margin setup

\setlength{\voffset}{0.05in}
\setlength{\paperwidth}{8.5in}
\setlength{\paperheight}{11in}
\setlength{\headheight}{0in}
\setlength{\headsep}{0in}
\setlength{\textheight}{10in}
\setlength{\topmargin}{-0.25in}
\setlength{\textwidth}{7in}
\setlength{\topskip}{0in}
\setlength{\oddsidemargin}{-0.25in}
\setlength{\evensidemargin}{-0.25in}
%-----------------------------------------------------------
\usepackage{shading}
\usepackage{changepage}
\pagestyle{empty}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

%-----------------------------------------------------------
%Custom commands
\newcommand{\indented}[1]{
    \begin{adjustwidth}{1cm}{}
        #1
    \end{adjustwidth}
}
\newcommand{\sectionline}{
    \noindent\rule[0.5ex]{\linewidth}{0.5pt}
}

\newcommand{\resitem}[1]{\item #1 \vspace{-3pt}}
\newcommand{\resheading}[1]{
    {\large \textbf{#1}}
    \sectionline
    %{\large \parashade[.8]{sharpcorners}{\textbf{\underline{#1}}}} %\vphantom{p\^{E}}}}}
}
\newcommand{\colfill}{@{\extracolsep{\fill}}}
\newcommand{\ressubheading}[4]{
\begin{tabular*}{6.5in}{l\colfill r}
		\textbf{#1} & #2 \\
		\textit{#3} & \textit{#4} \\
\end{tabular*}\vspace{-6pt}}

%-----------------------------------------------------------


\input{glyphtounicode}
\pdfgentounicode=1
\begin{document}
\begin{center}
\textbf{\Large Lucas Saldyt}
\end{center}
\begin{tabular*}{7in}{l \colfill r}
lucassaldyt@gmail.com & http://github.com/LSaldyt\\
% \hline
505-506-1245 & Mesa, Arizona \\
\end{tabular*}
\\

\vspace{0.1in}

\resheading{Education}
\begin{itemize}
\item
    \ressubheading{Barrett, The Honors College. Arizona State University}{Tempe, Arizona}{Bachelors of Computer Science, GPA: (3.7)}{Sep. 2017 - Current}
\item
    \ressubheading{MIT Open Courseware}{Online}{Supplementary Courses: assignments at github.com/LSaldyt}{Ongoing}
	\begin{itemize}
            \resitem{Data Structures and Algorithms, Quantum Algorithmic Complexity, Quantum Mechanics, Artificial Intelligence (Winston), Artificial General Intelligence (Fridman), Society of Mind, Computer Security, Information Theory}
	\end{itemize}

\end{itemize}


\resheading{Experience}
\begin{itemize}
 \item
     \ressubheading{NASA (National Aeronautics and Space Administration)}{Cape Canaveral, Florida}{Software Engineering Intern}{Jun. 2019 - Aug 2019}
 	\begin{itemize}
        \resitem{Benchmarked and optimized safety-critical live validation system for Launch Control System}
 		\resitem{Published abstract documenting software improvements made during the summer}
 	\end{itemize}
 \item
     \ressubheading{Sandia National Laboratories}{Albuquerque, New Mexico}{Quantum Computation Intern}{Jun. 2015 - Sep. 2018 (3 Summers)}
 	\begin{itemize}
        \resitem{Developed high-fidelity quantum benchmarking (Gate Set Tomography) software}
 		\resitem{Created a distributed high-performance simulation, verification, and data analysis software}
        \resitem{Oversaw porting entire codebase (over 1 million lines) to Python3.x}
 	\end{itemize}
 \item
     \ressubheading{The Fluid Analogies Research Group}{Remote (paid)}{Cognitive Science Intern}{Oct. 2016 - Sep. 2018}
 	\begin{itemize}
 		\resitem{Revitalization of Douglas Hofstadter's ``copycat'' cognitive model}
 		\resitem{Statistical analysis and comparison of various models to human data}
 	\end{itemize}
 \item
     \ressubheading{Dr. Carlos Castillo-Chavez's Complex Systems Research Group}{Tempe, Arizona}{Mathematics Intern}{Oct. 2018 - Current}
 	\begin{itemize}
 		\resitem{Math and computer modeling of ant nest choice and alarm propogration}
 	\end{itemize}
 \item
     \ressubheading{Unitary Fund}{Remote (paid)}{Quantum Software Researcher}{Jun. 2018 - Current}
 	\begin{itemize}
            \resitem{Prototyping of a quantum programming language, called ``Curry''}
            \resitem{Presentation in Brussels, Belgium at the FOSDEM Quantum Computing Conference}
 	\end{itemize}
 % \item
 %     \ressubheading{Fulton Undergraduate Research Initiative (Under Dr. Ajay Bansal)}{Tempe, Arizona}{Machine Learning Researcher}{Sep. 2018 - Current}
 % 	\begin{itemize}
 % 		\resitem{Analysis of Kolmogorov complexity with respect to machine learning}
 % 	\end{itemize}
 % \item
 % 	\ressubheading{Company}{Location}{Title}{Date}
 % 	\begin{itemize}
 % 		\resitem{Tasks}
 % 	\end{itemize}
 \item
     \ressubheading{Los Alamos National Laboratories}{Albuquerque, New Mexico}{Quantum Computation Intern (Shadow)}{April 2017}
 	\begin{itemize}
 		\resitem{Benchmarking the knapsack problem on LANL's DWave and IBM's 5-qubit machine}
 	\end{itemize}
\end{itemize}

\resheading{Skills}
\begin{description}
    \item[Programming Languages:] 
        Python, C++, Clojure, Java, Haskell
    \item[Operating Systems:]
        Linux (Arch, Redhat, Ubuntu), MacOS X, Windows
    \item[Applications:]
        Vim, \LaTeX, Jupyter Notebook, MatLab, Autodesk design, Office suites
    \item[Libraries:]
        tensorflow, pandas, seaborn, numpy, scikit learn
    %% \item[Exposed Languages:] C++, Python\ldots
    \item[Natural Languages:] 
        English, Ukranian, Spanish

%\item[Miscellaneous:]
%software configuration management, strong verbal and written communication skills, excellent troubleshooting and debugging skills, exceptional problem solving skills, good teams skills
\end{description}

\newpage

\resheading{Projects}
\begin{itemize}
\item
    \ressubheading{pyGSTi}{https://github.com/pyGSTio/pyGSTi}{Sandia National Labs}{2015 - Current}
	\begin{itemize}
            \resitem{Quantum Gate Set Tomography in Python. I am the second highest contributor with over 700 commits}
	\end{itemize}
\item
    \ressubheading{Curry}{https://github.com/LSaldyt/curry}{Unitary Fund}{2018 - Current}
	\begin{itemize}
            \resitem{A quantum programming language built ontop of Rigetti pyquil. I lead the project, organizing a small team of software developers through the github issues and project system}
	\end{itemize}
%% \item
%%     \ressubheading{kuiper}{https://github.com/kuiper/kuiper}{Unitary Fund}{2019 - Current}
%% 	\begin{itemize}
%%             \resitem{A ``quantum game'' based off of asteroids}
%% 	\end{itemize}
\item
    \ressubheading{Vorpal}{https://github.com/LSaldyt/vorpal}{Independent}{Dec. 2017}
	\begin{itemize}
            \resitem{A research and collaboration website, written in Clojure}
	\end{itemize}
\item
    \ressubheading{Nova}{https://github.com/LSaldyt/nova}{Independent}{Oct. 2017}
	\begin{itemize}
            \resitem{An Alexa-like assistant on Linux}
	\end{itemize}
\item
    \ressubheading{Cryptometric}{https://github.com/LSaldyt/cryptometric}{Independent}{Oct. 2017}
	\begin{itemize}
            \resitem{A server app that sends cryptocurrency statistics to a mobile phone by text}
	\end{itemize}
\end{itemize}

\resheading{Awards}
\begin{tabular*}{6.5in}{l@{\extracolsep{\fill}}r}
        ASU New American University Scholarship (\$14,000 annually) & 2017 \\
        ASU Discovery Fellowship (\$5,000)                          & 2019 \\
        Fluid Analogies Research Grant (\$5,000)                    & 2017 \\
        FURI Research Grant (\$3,000)                               & 2017 \\
        Unitary Fund Research Grant (\$2,200)                       & 2018 \\
\end{tabular*}

\vspace{0.3in}
\resheading{Interests}
\begin{description}
 \item[Academic:] Quantum Computing, Cognitive Science, Artificial Intelligence, Computer Science, Mathematics, Software Engineering
 \item[Sports:] Okinawan Karate
 \item[Musical:] Playing classical guitar and piano, composing music
 \item[Other:] Writing novels (I have completed two, as well as some short stories and poetry)
\end{description}

\end{document}
